Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
Intro restructuring
Change to percentage for ratings

## Class Outline

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students. A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.

@@

@@

## Sample size determination and statistical approach

After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well.

@@

Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.

## Individual Replications

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
replication rating `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

>>>>

## Study Selection

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students. A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.

@@

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.

@@

## Statistical approach

@@

@@

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original: `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.
